---
title: "Analysis by Albert"
output: html_notebook
---


# Loading Data
```{r}
library(class)
first<-read.csv(file="C:/Users/alber/Downloads/Classes/Stat 385/final project/Dfirst.csv",header=TRUE)
second<-read.csv(file="C:/Users/alber/Downloads/Classes/Stat 385/final project/Dsecond.csv",header=TRUE)
third<-read.csv(file="C:/Users/alber/Downloads/Classes/Stat 385/final project/Dthird.csv",header=TRUE)


```
## Figure out overlapping column names
```{r}
second <- second[,which(colnames(second)%in%colnames(first)==FALSE)]
third <- third[,which(colnames(third)%in%colnames(first)==FALSE&colnames(third)%in%colnames(second)==FALSE)]
third <- third[,which(colnames(third)%in%colnames(second)==FALSE)]
data = cbind(first,second,third)
compact_data <- cbind(first[,c(1,2,6,10,14)],second[,c(1,5,9,13,17)])
compact_data$speed.mean <- third[,1]
```
# Save abridged data into a csv
```{r}
write.csv(compact_data,"C:/Users/alber/Downloads/Classes/Stat 385/final project/compact_data.csv")
```
<<<<<<< HEAD


# Normalization Functions
=======
# Save complete data into a csv
```{r}
complete_data <- cbind(first,second,third)
write.csv(complete_data,"C:/Users/alber/Downloads/Classes/Stat 385/final project/complete_data.csv")
```


# Normalization Functions
## Normalize by max or use z-score

```{r}
max_normalization<-function(x)
{
  norms<-(x-min(x))/(max(x)-min(x))
  return(norms)
}

z_normalization <-function(x){
  mu <- mean(x)
  sigma <- sd(x)
  z <- (x-mu)/sigma
  return(z)
}
```
```{r}
max_normal <- compact_data
max_normal[,-5] <- sapply(compact_data[,-5],max_normalization)

z_normal <- compact_data
z_normal[,-5] <- sapply(compact_data[,-5],z_normalization)
```
<<<<<<< HEAD
# Save normalized data to csv
=======

```{r}
max_complete <- complete_data
max_complete[,-14] <- sapply(complete_data[,-14],max_normalization)

z_complete <- complete_data
z_complete[,-14] <- sapply(complete_data[,-14],z_normalization)
```

# Save normalized abridged data to csv
>>>>>>> 80a915b722098eb8c7ee66f89abec6773a491efe
```{r}
write.csv(max_normal,"C:/Users/alber/Downloads/Classes/Stat 385/final project/max_normal.csv")
write.csv(z_normal,"C:/Users/alber/Downloads/Classes/Stat 385/final project/z_normal.csv")
```
<<<<<<< HEAD

=======
# Save normalized complete data to csv
```{r}
write.csv(max_complete,"C:/Users/alber/Downloads/Classes/Stat 385/final project/max_complete.csv")
write.csv(z_complete,"C:/Users/alber/Downloads/Classes/Stat 385/final project/z_complete.csv")
```

# Load normalized data
```{r}
z_normal<-read.csv(file="C:/Users/alber/Downloads/Classes/Stat 385/final project/z_normal.csv",header=TRUE)
#max_normal<-read.csv(file="C:/Users/alber/Downloads/Classes/Stat 385/final project/max_normal.csv",header=TRUE)

z_complete<-read.csv(file="C:/Users/alber/Downloads/Classes/Stat 385/final project/z_complete.csv",header=TRUE)
#max_complete<-read.csv(file="C:/Users/alber/Downloads/Classes/Stat 385/final project/max_complete.csv",header=TRUE)
```



## Data set exploration

```{r}
#boxplot(compact_data$android.sensor.game_rotation_vector.mean~compact_data$target)


kmeans.model2<-kmeans(z_normal[1:4000,-5],5)
table(kmeans.model2$cluster,z_normal$target[1:4000])
```
```{r}
plot(z_normal[,c(9:11)], col=kmeans.model2$cluster, main="K-means clustering")

#kmeans.model<-kmeans(max_normal[1:4000,-5],5)
#table(kmeans.model$cluster,max_normal$target[1:4000])

```

# Useful columns: 1,3,4,5,9,10,12,15,19,21,27,31,35,38
```{r}
#for (i in 1:13){boxplot(z_complete[,i]~z_normal$target)}
#for (i in 15:38){boxplot(z_complete[,i]~z_normal$target)}
```
```{r}
kmeans.model2<-kmeans(z_complete[1:4000,c(1,3,4,5,9,10,12,15,19,21,27,31,35,38)],5)
table(kmeans.model2$cluster,z_complete$target[1:4000])
table(z_complete$target[1:4000])
table(kmeans.model2$cluster)
```
```{r}
kmeans.model2<-kmeans(max_complete[1:4000,c(1,3,4,5,9,10,12,15,19,21,27,31,35,38)],5)
table(kmeans.model2$cluster,max_complete$target[1:4000])
table(max_complete$target[1:4000])
table(kmeans.model2$cluster)
```















# Variable manipulation
```{r}
z_complete<-read.csv(file="C:/Users/alber/Downloads/Classes/Stat 385/final project/z_complete.csv",header=TRUE)
z_complete$target <- as.factor(z_complete$target)
#complete<-read.csv(file="C:/Users/alber/Downloads/Classes/Stat 385/final project/complete_data.csv",header=TRUE)
#complete$target <- as.factor(complete$target)
#max_complete$target <- as.factor(max_complete$target)
```

```{r}
z_complete$LAM <- z_complete$android.sensor.linear_acceleration.mean^2
z_complete$G <- z_complete$android.sensor.gyroscope.mean^2
z_complete$SM <- z_complete$speed.mean^2


```
```{r}
plot(z_complete$speed.mean,z_complete$android.sensor.accelerometer.std,col=z_complete$target)
#plot(z_complete$LAM[z_complete$target=="Still"],z_complete$GC[z_complete$target=="Still"])
legend("topright", legend=levels(z_complete$target), pch=1,col=z_complete$target)
```

# Decision Tree
```{r}
library(rpart)
library(rpart.plot)
training_data <- z_complete[1:4000,]
test <- z_complete[4001:5893,]
```

# Post-pruning
```{r}
treefit2<-rpart(target~., data=training_data, method="class", parms=list(split = "information"),control = rpart.control(minsplit=5, cp=0))
bestcp <- treefit2$cptable[which.min(treefit2$cptable[,"xerror"]),"CP"]
tree.pruned <- prune(treefit2, cp = bestcp)
```



```{r}
pred <- predict(tree.pruned,newdata=test, type="class")
truth<-test$target
table(truth,pred)
#table(pred)
#table(truth)
correct <- 0
for (i in 1:5) {
  correct <- correct + table(truth,pred)[i,i]
}
correct/1893
pred <- predict(tree.pruned,newdata=training_data, type="class")
truth<-training_data$target
correct <- 0
for (i in 1:5) {
  correct <- correct + table(truth,pred)[i,i]
}
#correct/4000

```
# Analyze most important variables
```{r}
tree.pruned$variable.importance
#tree.pruned$splits
#colnames(z_complete)
```
```{r}
names <- c("android.sensor.linear_acceleration.mean","android.sensor.accelerometer.std","android.sensor.gyroscope.mean","speed.mean","speed.max","speed.min","android.sensor.linear_acceleration.max","android.sensor.linear_acceleration.min","android.sensor.accelerometer.max","android.sensor.accelerometer.min","sound.mean","sound.min","android.sensor.gyroscope.max","android.sensor.game_rotation_vector.mean","android.sensor.gyroscope.std","sound.max","android.sensor.game_rotation_vector.min","android.sensor.rotation_vector.min","android.sensor.game_rotation_vector.max","time","android.sensor.gyroscope_uncalibrated.mean","android.sensor.rotation_vector.max","android.sensor.rotation_vector.mean","speed.std","android.sensor.orientation.mean","android.sensor.orientation.min","android.sensor.accelerometer.mean","android.sensor.orientation.max","sound.std","android.sensor.gyroscope_uncalibrated.max","android.sensor.gyroscope_uncalibrated.std","android.sensor.gyroscope_uncalibrated.min", "android.sensor.orientation.std","android.sensor.linear_acceleration.std","android.sensor.gyroscope.min","android.sensor.game_rotation_vector.std","android.sensor.rotation_vector.std")

b <- c()
for (i in 1: length(names)){
  b[i] <- which(colnames(z_complete)==names[i])
}
```

# Determine the contribution of each variable
```{r}
#top 8 c(5,6,14,23,24,25,35,36,37)
#top 10 c(3,4,5,6,14,23,24,25,35,36,37)
#delete less useful variables: c(-7,-26,-18,-34)
test_correctness <- c()
train_correctness <- c()
for (i in 1:36){
  k <- 37-i
training2 <- training_data[,c(b[1:k],14)]
test2 <- test[,c(b[1:k],14)]

treefit3<-rpart(target~., data=training2, method="class", parms=list(split = "information"),control = rpart.control(minsplit=5, cp=0))
bestcp2 <- treefit3$cptable[which.min(treefit3$cptable[,"xerror"]),"CP"]
tree.pruned2 <- prune(treefit3, cp = bestcp2)

pred2 <- predict(tree.pruned2,newdata=test2, type="class")
truth2<-test2$target
table(truth2,pred2)

correct <- 0
for (m in 1:5) {
  correct <- correct + table(truth2,pred2)[m,m]
}
test_correctness[i] <- correct/1893
pred2 <- predict(tree.pruned2,newdata=training2, type="class")
truth2<-training2$target
correct <- 0
for (j in 1:5) {
  correct <- correct + table(truth2,pred2)[j,j]
}
train_correctness[i] <- correct/4000
}
```
```{r}
plot(rev(train_correctness),xlab = "Number of Variables Used",ylab = "Accuracy", main="Accuracy vs. Variables Used", col="purple",ylim=c(0.55,1))
points(rev(test_correctness),pch = 2,col="blue")
legend("bottomright", legend=c("Test", "Train"), pch=c(1, 2),col = c("purple", "blue"))
```

