---
title: "LogisticRegression"
author: "Bella Patel"
date: "4/18/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
knitr::opts_knit$set(root.dir = "/Users/bellapatel/stat385/")
```

## Data Preparation

Read and prepare data for regressions by creating test and training datasets.

```{r}
normal <- read.csv("max_normal.csv")
set.seed(2021)
sample <- sample(nrow(normal), 4000)
training <- normal[sample, ]
training1 <- training
test <- normal[-sample,]
```

## Extract columns

Extract columns as vectors to use in regressions.

```{r}
acceleration <-as.double(training1[,2]) # android.sensor.accelerometer.mean
gyroscope <-as.double(training1[,3]) # android.sensor.gyroscope.mean
sound <- as.double(training1[,4])
gamerotation <- as.double(training1[,6])
linacc <- as.double(training1[,8]) #android.sensor.linear_acceleration.mean
orientation <- as.double(training1[,9])
rotationvec <- as.double(training1[,10])
speed <- as.double(training1[,11]) # speed.mean
```

## Pairwise Logistic Regressions

Logistic regression works for binary targets. Combine several classes into two classes, then apply binary classification iteratively for each target.

```{r}
# bus
training1 <- training
training1$target <- as.character(training1$target)
training1$target[training1$target != "Bus"] <- 0
training1$target[training1$target == "Bus"] <- 1
training1$target <- as.integer(training1$target)
target <- as.integer(training1[,5])

logisticbus <-glm(target~acceleration*sound+gyroscope*speed+sound*orientation*rotationvec*gamerotation+gamerotation*linacc+orientation*linacc*gyroscope, family="binomial")

# train
training1 <- training
training1$target <- as.character(training1$target)
training1$target[training1$target != "Train"] <- 0
training1$target[training1$target == "Train"] <- 1
training1$target <- as.integer(training1$target)
target <- as.integer(training1[,5])

logistictrain <-glm(target~acceleration+gyroscope*speed*sound+linacc*sound+sound*speed*rotationvec+sound+orientation*sound, family="binomial") 

# car
training1 <- training
training1$target <- as.character(training1$target)
training1$target[training1$target != "Car"] <- 0
training1$target[training1$target == "Car"] <- 1
training1$target <- as.integer(training1$target)
target <- as.integer(training1[,5])

logisticcar <-glm(target~speed*sound+acceleration*sound+gyroscope*linacc*speed+rotationvec+orientation*speed*rotationvec, family="binomial") 

training1 <- training
training1$target <- as.character(training1$target)
training1$target[training1$target != "Still"] <- 0
training1$target[training1$target == "Still"] <- 1
training1$target <- as.integer(training1$target)
target <- as.integer(training1[,5])

logisticstill <-glm(target~gyroscope*sound*acceleration+speed*sound*orientation*linacc+linacc*sound+rotationvec*sound*speed, family="binomial")

# walking
training1 <- training
training1$target <- as.character(training1$target)
training1$target[training1$target != "Walking"] <- 0
training1$target[training1$target == "Walking"] <- 1
training1$target <- as.integer(training1$target)
target <- as.integer(training1[,5])

logisticwalking <-glm(target~acceleration+gyroscope+linacc*sound+orientation*speed*sound+speed*sound*rotationvec, family="binomial") 
```

## R^2 for logistic regressions

R-squared is "goodness of fit"; how much of your data is explained by the data. Find R-squared by measuring the ratio of the deviance in your model to the null. Higher the R-squared, the better the model.

```{r}
with(summary(logisticwalking), 1 - deviance/null.deviance) # walking
with(summary(logisticbus), 1 - deviance/null.deviance) # bus
with(summary(logistictrain), 1 - deviance/null.deviance) # train
with(summary(logisticstill), 1 - deviance/null.deviance) # still
with(summary(logisticcar), 1 - deviance/null.deviance) # car
```

## Testing the logisitic regressions

Loop through all the rows of the test data. Calculate probability of each mode of selection. Classify as highest probability.

```{r}
levels <- c("Walking", "Bus", "Still", "Train", "Car")
predictions <- c()

for (row in 1:nrow(test))
{
  acceleration1 <-as.double(test[,2][row]) # android.sensor.accelerometer.mean
  gyroscope1 <-as.double(test[,3][row]) # android.sensor.gyroscope.mean
  sound1 <- as.double(test[,4][row])
  gamerotation1 <- as.double(test[,6][row])
  linacc1 <- as.double(test[,8][row]) #android.sensor.linear_acceleration.mean
  orientation1 <- as.double(test[,9][row])
  rotationvec1 <- as.double(test[,10][row])
  speed1 <- as.double(test[,11][row]) # speed.mean

  
  busprob <- predict(logisticbus, newdata=data.frame(acceleration = acceleration1,gyroscope = gyroscope1, sound = sound1, gamerotation = gamerotation1, linacc = linacc1, orientation = orientation1, rotationvec = rotationvec1, speed = speed1), type="response")
  walkingprob <- predict(logisticwalking, newdata=data.frame(acceleration = acceleration1,sound = sound1, gyroscope = gyroscope1, linacc = linacc1, orientation = orientation1, rotationvec = rotationvec1, speed = speed1), type="response")
  stillprob <- predict(logisticstill, newdata=data.frame(gyroscope = gyroscope1, acceleration = acceleration1, linacc = linacc1, orientation = orientation1, speed = speed1, rotationvec = rotationvec1, sound = sound1), type="response")
  trainprob <- predict(logistictrain, newdata=data.frame(acceleration = acceleration1, speed = speed1,gyroscope = gyroscope1, linacc = linacc1, sound = sound1, orientation = orientation1, rotationvec = rotationvec1), type="response")
  carprob <- predict(logisticcar, newdata=data.frame(acceleration = acceleration1, speed = speed1, linacc = linacc1, sound = sound1, orientation = orientation1, rotationvec = rotationvec1, gyroscope = gyroscope1), type="response")
  
  predictionprobs <- c(walkingprob, busprob, stillprob, trainprob, carprob)
  predictions[row] = levels[which.max(predictionprobs)]
}
```

# Test accuracy

```{r}
correct = 0
for (i in 1:length(predictions)){
  if(test$target[i] == predictions[i])
    correct <- correct + 100
}
correct/length(predictions)
```